Network Concurrency Control Done In Band

### 2015-05-30 inband-sync.tex
small

%[[PK sorry for stubborness :)
\title{On the Synchronization Power of the OpenFlow Data Plane}
%\\ {\Large Towards Atomic Transactions In-Band}}
%]]

@@

\author{
Liron Schiff\thanks{Supported by the European Research Council (ERC) Starting Grant no. 259085 and by the Israel Science Foundation Grant no.~1386/11.} $^1$,
Stefan Schmid$^2$, Petr Kuznetsov$^3$ \\
\small $^1$ Tel Aviv University, Israel; $^2$ TU Berlin \& T-Labs,
Germany; $^3$ T\'el\'ecom ParisTech, France
}

@@

\begin{abstract}
Control planes of forthcoming Software-Defined Networks (SDNs)
will be \emph{distributed}: to ensure availability and fault-tolerance,
to improve load-balancing, and to reduce overheads,
control modules operating on the data plane should be physically distributed.
%a redundant control plane
%can ensure a high availability, and a spatially distributed
%control plane allows to handle time-critical dataplane
%events close to their origins.
%[[PK this is a contraversial point, not important for us
%Moreover, an SDN may be managed by multiple administrators simultaneously.
%]]
However, %a distributed control plane also introduces
%new challenges,
in order to guarantee \emph{consistency} of network operation, actions
performed on the data plane by different controllers may need to be \emph{synchronized},  which is a
 nontrivial task.
%[[PK sounds contradicting to the fact that such systems already exist
%However, not much is known today about how to implement
%such a distributed control plane.
%]]
%
In this paper, we propose a synchronization
framework for control planes  based on the well-known concept of
\emph{transactions}.
%
A transaction aggregates a sequence
of control messages and specific synchronization primitives,
providing all-or-nothing semantics.
We argue that a powerful transactional interface should and can be implemented \emph{inband}, using 
standard OpenFlow commands on the data plane configuration.
%Indeed, recent OpenFlow versions already come with useful but primitive
%features, in particular \emph{bundling} and \emph{rule-overlap checks}.
%In particular, we present a
%transactional interface which supports arbitrary atomic
%transactions
%over the switch configuration space:
%Our transactions
%can include complex notions of conflicts (beyond flow overlap checks),
%as well as computations and multiple controller interactions.
We discuss how to use our synchronization framework to implement
 consistent policy compositions and replicated control plane services.
\end{abstract}

>>>>

%[[PK sorry for stubborness :)
%\title{On the Synchronization Power of the OpenFlow Data Plane}
\title{Network Concurrency Control Done In Band}
%\\ {\Large Towards Atomic Transactions In-Band}}
%]]

@@

\author{
Liron Schiff$^1$, % \thanks{Supported by the European Research Council (ERC) Starting Grant no. 259085 and by the Israel Science Foundation Grant no.~1386/11.} $^1$,
Stefan Schmid$^2$, Petr Kuznetsov$^3$ \\
\small $^1$ Tel Aviv University, Israel; $^2$ TU Berlin \& T-Labs,
Germany; $^3$ T\'el\'ecom ParisTech, France
}

@@

\begin{abstract}
Control planes of forthcoming Software-Defined Networks (SDNs)
will be \emph{distributed}: to ensure availability and fault-tolerance,
to improve load-balancing, and to reduce overheads,
control modules operating on the data plane should be physically distributed.
%a redundant control plane
%can ensure a high availability, and a spatially distributed
%control plane allows to handle time-critical dataplane
%events close to their origins.
%[[PK this is a contraversial point, not important for us
%Moreover, an SDN may be managed by multiple administrators simultaneously.
%]]
However, %a distributed control plane also introduces
%new challenges,
in order to guarantee \emph{consistency} of network operation, actions
performed on the data plane by different controllers may need to be \emph{synchronized},  which is a
 nontrivial task.
%[[PK sounds contradicting to the fact that such systems already exist
%However, not much is known today about how to implement
%such a distributed control plane.
%]]
%
In this paper, we propose a synchronization
framework for control planes  based on the well-known concept of
\emph{transactions}.
%
A transaction aggregates a sequence
of control messages and specific synchronization primitives,
providing all-or-nothing semantics.
We argue that a powerful transactional interface should and can be implemented \emph{inband}, using 
standard OpenFlow commands on the data plane configuration.
%Indeed, recent OpenFlow versions already come with useful but primitive
%features, in particular \emph{bundling} and \emph{rule-overlap checks}.
%In particular, we present a
%transactional interface which supports arbitrary atomic
%transactions
%over the switch configuration space:
%Our transactions
%can include complex notions of conflicts (beyond flow overlap checks),
%as well as computations and multiple controller interactions.
We discuss how to use our synchronization framework to implement
 consistent policy composition and fault-tolerant control-plane applications.
\end{abstract}
